\textbf{NBA Party}

### 2017-06-10 init_model.rnw
Added dot-plot of continuous-party by team-location.

HOURS <- 24
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians), 0)]

@@

nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & nhours.lgame <= 24]

m0 <- glm(outcome == 'W' ~ party.discrete + lag.chg.pos + log(travel.dist+1)*ew + 
             nhours.lgame + I(hour(date)) + I(team==location),
         data = nba.lines[season < 2017], family = 'binomial',
         na.action = 'na.exclude')

m1 <- glm(outcome == 'W' ~ party + lag.chg.pos + log(travel.dist+1)*ew + 
             nhours.lgame + I(hour(date)) + I(team==location),
         data = nba.lines[season < 2017], family = 'binomial',
         na.action = 'na.exclude')

@@

## nba.lines[,.N/2,by=list(season)]
## stargazer(m)

@@

lm(team.pts.admitted ~ party + lag.chg.pos + log(travel.dist+1) + nhours.lgame, data=data[last.game.loc!=team] %>% na.omit) %>% summary

### Points  allowed as afunction of last game location (by party)
nba.lines[, demeaned.pts.admitted := team.pts.admitted - mean(team.pts.admitted), by = list(season, team)]
nba.lines[, mean(demeaned.pts.admitted), by = list(last.game.loc, party.discrete)][order(V1)]
tmp <- nba.lines[, list(demeaned.pts.admitted = mean(demeaned.pts.admitted)), 
                 by = list(last.game.loc, party)][order(demeaned.pts.admitted)]
plot(x=jitter(tmp$party),y=tmp$demeaned.pts.admitted)
abline(lm(demeaned.pts.admitted ~ party, data=tmp))
#stargazer(m, style = 'qje', single.row = T)
## stargazer(m)

@@

m3 <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + log(travel.dist+1) + weekend,
         data = mlb.lines, family = 'binomial')
summary(m3)
#stargazer(m0, m1, m2, m3, single.row = T)
@

>>>>

HOURS <- 24
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & 
                nhours.lgame <= HOURS & 
                last.game.loc != team]

@@

m0 <- glm(outcome == 'W' ~ party.discrete + lag.chg.pos + log(travel.dist+1)*ew + 
             nhours.lgame + I(hour(date)) + I(team==location),
         data = nba.lines[season < 2017 & !is.na(party)], family = 'binomial',
         na.action = 'na.exclude')

m1 <- update(m0, . ~ party + . - party.discrete)

@@

## nba.lines[,.N/2,by=list(season)]
stargazer(m0, m1, covariate.labels = c('party discrete', 'party continuous', 'lag changes in posession', 'logged travel distance', 'east-west travel direction', 'number hours rest time', 'time of game during day', 'home team effect', 'logged travel distance * east-west', 'Constant'),
          dep.var.labels = 'Meet the Spread')

tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
                 by = team][order(party.continuous)][!is.na(party.continuous)]

##################################################
### Dot plot of Party-Continuous by Team Location
##################################################
pdf('writing/Party_by_Team_Location.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location',
     ylab = 'Log Avg of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
## text(x = ticks, y = 1.25, labels = tmp$team, srt = 90)
axis(side = 2)
dev.off()

@@

mpa <- lm(team.pts.admitted ~ party + lag.chg.pos + log(travel.dist+1) + nhours.lgame, 
   data=nba.lines[last.game.loc!=team] %>% na.omit)
mpo <- update(mpa, team.pts.scored ~ .)

### Points  allowed as afunction of last game location (by party)
nba.lines[, demeaned.pts.admitted := team.pts.admitted - mean(team.pts.admitted), by = list(season, team)]
nba.lines[, mean(demeaned.pts.admitted), by = list(last.game.loc, party.discrete)][order(V1)]
mpa1 <- lm(demeaned.pts.admitted ~ party.discrete, data = nba.lines)
#stargazer(mpa1, mpa, mpo, single.row=T)

tmp <- nba.lines[, list(demeaned.pts.admitted = mean(demeaned.pts.admitted)), 
                 by = list(last.game.loc, party)][order(demeaned.pts.admitted)]
plot(x=jitter(tmp$party),y=tmp$demeaned.pts.admitted)
abline(lm(demeaned.pts.admitted ~ party, data=tmp))
#stargazer(m, style = 'qje', single.row = T)
## stargazer(m)

@@

m3 <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + log(travel.dist+1) + weekend,
         data = mlb.lines, family = 'binomial')
summary(m3)

mlb.lines[, party.discrete := grepl("(los angeles)|(new york)", last.game.loc) & ndays.lgame == 1 & weekend == T]
#stargazer(m0, m1, m2, m3, single.row = T)
@
